### 2021-05-17 main.tex
more main

%6) What are the directions for follow-up research?  (24 words)
We hope that it becomes part of a standardization effort and that modelers adopt the benefits of provenance when considering or creating simulation models.

@@

We revise a provenance ontology for simulation studies of cellular biochemical models.
Provenance information is useful for understanding the creation of a simulation model because it not only contains information about the entities and activities that have led to a simulation model, but also the relations, all of which can be visualized.
It provides additional structure as research questions, assumptions, and requirements are singled out and explicitly related along with data, qualitative models, simulation models, and simulation experiments through a small set of predefined but extensible activities.
% TODO the above sentence doesn't make sense

@@

% What is our goal of this publication? And what is the Wnt signaling pathway?
In this publication, we will identify and structure relevant information needed for the provenance of simulation studies and elucidate how a family of simulation models can be established through relating the models to each other.
As a case study, we will concentrate on 19 simulation studies of the \wnt{}/\bcat{} signaling pathway.
Among the different \wnt{} signaling pathways, the canonical \wnt{} or \wnt{}/\bcat{} signaling pathway is the most intensively studied one, \textit{in vitro}~\cite{MacDonald2009} as well as \textit{in silico}~\cite{Lloyd-Lewis2013}.
This pathway is considered to be one of the key pathways in development and regeneration, including cell fate, cell proliferation, cell migration and adult homeostasis~\cite{Steinhart2018, Giles2003}.
In deregulated forms, it is involved in human cancers and developmental disorders~\cite{Clevers2012, Logan2004}.

@@

Second, we will discuss our findings applying our specialization of PROV-DM and demonstrate the relationships as well as specific features of the provenance information of the 19 \wnt{} simulation studies covered in this publication.
% "findings applying"?

@@

%Introduction to our specialization of PROV-DM
The specialization of PROV-DM, which was introduced by Ruscheinski et al. (2018)~\cite{Ruscheinski2018}, is being revised and refined.
% "is being"? Maybe "was"?
For capturing provenance information of simulation studies of cellular biochemical simulation models and relating these, we are defining and using
% again, is the tense current or past? "we are defining" or "we defined"?
\begin{inparaenum}[a)]
\item specific types of entities and activities and
\item specific relations with their roles and constraints.
\end{inparaenum}
During the process of collecting provenance information from these studies, we identified these types and relations as well as information that is useful for describing them.
% I think the above sentences could be reorganized to simply things
Our final set of entities, activities, and relations is shown in Table~\ref{tab:entitiesandactivities}.
Each entity and activity has already been mentioned for provenance, modeling or documentation purposes, or experiment design of simulation studies~\cite{Ruscheinski2017, Balci2012, Yilmaz2016, Monks2018, Bergmann2014, Carusi2012, Erdemir2012, Lorig2017, Ruscheinski2018, Waltemath2011, Wilsdorf2020b}, but they have not all been used together.

>>>>

%6) What are the directions for follow-up research?  (24 words)
We hope that it becomes part of a standardization effort and that modelers adopt the benefits of provenance when considering or creating simulation models.
% TODO what do you mean by "it" here?

@@

We revise a provenance ontology for simulation studies of cellular biochemical models.
Provenance information is useful for understanding the creation of a simulation model because it not only contains information about the entities and activities that have led to a simulation model, but also the relations, all of which can be visualized.
It provides additional structure because research questions, assumptions, and requirements are singled out and explicitly related along with data, qualitative models, simulation models, and simulation experiments through a small set of predefined but extensible activities.

@@

% What is our goal of this publication? And what is the Wnt signaling pathway?
In this publication, we will identify and structure relevant information needed for the provenance of simulation studies and elucidate how a family of simulation models can be established through relating the models to each other.
% elucidate?
As a case study, we will concentrate on 19 simulation studies of the \wnt{}/\bcat{} signaling pathway.
Among the different \wnt{} signaling pathways, the canonical \wnt{} or \wnt{}/\bcat{} signaling pathway is the most intensively studied one, \textit{in vitro}~\cite{MacDonald2009} as well as \textit{in silico}~\cite{Lloyd-Lewis2013}.
This pathway is considered to be one of the key pathways in development and regeneration, including cell fate, cell proliferation, cell migration and adult homeostasis~\cite{Steinhart2018, Giles2003}.
In deregulated forms, it is involved in human cancers and developmental disorders~\cite{Clevers2012, Logan2004}.

@@

Second, we will discuss our findings applying our specialization of PROV-DM and demonstrate the relationships as well as specific features of the provenance information of the 19 \wnt{} simulation studies covered in this publication.
% TODO comma?

@@

%Introduction to our specialization of PROV-DM
The specialization of PROV-DM, which was introduced by Ruscheinski et al. (2018)~\cite{Ruscheinski2018}, has been revised and refined.
For capturing provenance information of simulation studies of cellular biochemical simulation models and relating these, we are defining and using
% again, is the tense current or past? "we are defining" or "we defined"?
\begin{inparaenum}[a)]
\item specific types of entities and activities and
\item specific relations with their roles and constraints.
\end{inparaenum}
During the process of collecting provenance information from these studies, we identified these types and relations as well as information that is useful for describing them.
% I think the above sentences could be reorganized to simply things
Our final set of entities, activities, and relations is shown in Table~\ref{tab:entitiesandactivities}.
Each entity and activity has already been mentioned for provenance, modeling or documentation purposes, or experiment design of simulation studies~\cite{Ruscheinski2017, Balci2012, Yilmaz2016, Monks2018, Bergmann2014, Carusi2012, Erdemir2012, Lorig2017, Ruscheinski2018, Waltemath2011, Wilsdorf2020b}, but they have not all been used together.
